---
title: "01 Data Prep"
author: "JungHwan Yang"
date: "March 26, 2015"
output: html_document
---

## This is Korean Presidential Debate 1 project.

To read the data without formatting errors, I had to read the text file in SPSS and saved in .sav; then read it from R.

```{r Read raw data}
library(foreign)

# path <- "Data//koprez1.sav" # All commas removed from this file
# d <- read.spss(path, use.value.labels = F, to.data.frame = T)
# 
# d[d == "\\N"] <- NA

# For quick transformation of df, convert the df into data table
library(data.table)
# d.table <- data.table(d)
# # Sort by time
# setorder(d.table, V2)
# d.table <- subset(d.table, V2 != "NA")
# # Subset two hours (2:20 hours)
# d2 <- subset(d.table,
#                as.POSIXct(V2) > '2012-12-04 10:30:00' &
#                as.POSIXct(V2) < '2012-12-04 13:30:00')
# rm(d);rm(d.table)
```

After restricting the data within two-hour range, number of case is 27,486.
### I saved the data as koprez1.RData. *Use this file when I need the full data*

http://rstudio-pubs-static.s3.amazonaws.com/1617_b9a9f37daa2d48d9be83ad0b91d7fdf4.html

http://www.ddokbaro.com/3695


In order to training machine, we need to hand code tweets--to test IRR and to make training and test sets.
J and Hyesun Choung coded the tweets.

```{r Human coding}
# set.seed(7)
# korandom1500 <- d2[sample(1:nrow(d2), 1500, replace = F), ]
# 
# write.xlsx(korandom1500, file="Data/korandom1500.xlsx")
```

TEST IRR

```{r}
# coding100 <- read.csv("Data/korandom100coding.csv") # This file contains 48 tweets of the second round coding (63-110)
# library(irr)
# kripp.alpha(t(as.matrix(coding100[,])), method = "nominal")
# # Alpha = .746, which isacceptable. So, coders coded other tweets.
```


Read handcded tweets (N = 1500)

(Paste codings in .sav file and open from .sav)

```{r}
# d.coded <- read.xlsx ("Data/korandom1500.xlsx", 1)
# d.coded <- subset(d.coded, select=-c(1,3)) #Remove vars not used

# Merge cells with some errors
d.coded$V3 <- paste(d.coded$V3, d.coded$V30, sep = ""); d.coded$V30 <- NULL
d.coded$V9 <- paste(d.coded$V9, d.coded$V90, sep = ""); d.coded$V90 <- NULL
```

```{r}
# Add time var
d.coded.2 <- 
  subset(d.coded,
         as.POSIXct(V2) > '2012-12-04 10:50:29' &
         as.POSIXct(V2) < '2012-12-04 13:04:01')
```

```{r}
library(KoNLP) # To analyze Korean language
library(tm)

# Make functions to clean texts using regular expression

# removeRT <- function(x) {
#     gsub("RT @[[:graph:]]*", "", x)
# }
# 
# removeMention <- function(x) {
#     gsub("@[[:graph:]]*", "", x)
# }
# 
# removeURL <- function(x) {
#     gsub("http://[[:graph:]]*", "", x)
# }

library(dplyr)
library(stringr)
# Create a function called cleanText that removes
cleanText <- function(text) {
 corpus.tmp <- text %>%
  str_replace_all("RT @|MT @", "RTATUSER") %>% #replace RT and MT into RTATUSER
  gsub("@[[:graph:]]*", "", .) %>% #remove @mentions
  str_replace_all("ATUSER", "") %>% #restore RT
  tolower(.) %>% #change into lowercase
  str_replace_all("[[:space:]]", " ") %>% #remove white space
  gsub("http://[[:graph:]]*", "", .) %>% #remove links
  gsub("([#])|[[:punct:]]", "\\1", .) #remove punctuations except hashtags. this may remove _ in username
 return(corpus.tmp)
}

# Apply clearText() to every line
d.coded.2$text <- sapply(d.coded.2$V3, cleanText)

### This part of extracting nouns are very unreliable and unstable
# Extract Nouns
# useSejongDic()

# useSystemDic()
# Update dictionary before extracting nouns
# mergeUserDic(data.frame(c("문재인","문죄인","리정희","안철수","다카키",
#                         "마사오", "다카키마사오", "#나는꼼수다", "문후보"),
#                         "ncn"))
# 
# tmp <- sapply(d.coded$text, function(x) {
#  paste(extractNoun(x), collapse = " ")
#  })
# 
# 
# # Update dictionary before extracting nouns
# mergeUserDic(data.frame(c("문재인","문죄인","리정희","안철수","다카키",
#                         "마사오", "다카키마사오", "#나는꼼수다", "문후보"),
#                         "ncn"))
# Create a word corpus
koCorpus <- Corpus(VectorSource(d.coded.2$text))
# koCorpus.C <- Corpus(VectorSource(d.coded$text[d.coded$Coding == "C"]))
# koCorpus.L <- Corpus(VectorSource(d.coded$text[d.coded$Coding == "L"]))
# koCorpus.M <- Corpus(VectorSource(d.coded$text[d.coded$Coding == "M"]))
#####
#####
#####

# Remove stopwords - Create a list of myStopwords
# myCorpus_ <- tm_map(myCorpus, removeWords, myStopwords)
ko.dtm <- data.frame(inspect(DocumentTermMatrix(koCorpus)))

# Merge humen coding of tweet ideology
ko.dtm <- 
  cbind(d.coded.2$Coding, ko.dtm)
names(ko.dtm)[1] <- "User_Ideology"

# Change the variable names of the hashtag DTM by replacing # with h.
names (ko.dtm) <-
  names(ko.dtm) %>%
  gsub("X.", "h.", .)

# Remove weird X
names (ko.dtm) <-
  names(ko.dtm) %>%
  gsub("X", "", .)

```


```{r}
# Manually stem document

### I should make this process more simple. Make a list of words in a separate file and let R code read it line by line.

# 국민
국민.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^국민*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^국민*", names(ko.dtm), value=T)))
ko.dtm$국민.stem <- 국민.stem
rm(국민.stem)

# 궁금
궁금.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^궁금*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^궁금*", names(ko.dtm), value=T)))
ko.dtm$궁금.stem <- 궁금.stem
rm(궁금.stem)

# 공산
공산.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^공산*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^공산*", names(ko.dtm), value=T)))
ko.dtm$공산.stem <- 공산.stem
rm(공산.stem)

# 나왔
나왔.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^나왔*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^나왔*", names(ko.dtm), value=T)))
ko.dtm$나왔.stem <- 나왔.stem
rm(나왔.stem)

# 날치기
날치기.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^날치기*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^날치기*", names(ko.dtm), value=T)))
ko.dtm$날치기.stem <- 날치기.stem
rm(날치기.stem)

# 남북관계
남북관계.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^남북관계*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^남북관계*", names(ko.dtm), value=T)))
ko.dtm$남북관계.stem <- 남북관계.stem
rm(남북관계.stem)

# 남쪽정부, 남한정부
남쪽정부.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^남쪽정부*", names(ko.dtm), value=T)], na.rm = T)
남한정부.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^남한정부*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^남쪽정부*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^남한정부*", names(ko.dtm), value=T)))
ko.dtm$남쪽정부.stem <- 남쪽정부.stem + 남한정부.stem
rm(남쪽정부.stem); rm(남한정부.stem)

# 내거티, 내가티
내거티.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^내거티*", names(ko.dtm), value=T)], na.rm = T)
내가티.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^내가티*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^내거티*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^내가티*", names(ko.dtm), value=T)))
ko.dtm$내거티.stem <- 내거티.stem + 내가티.stem
rm(내거티.stem); rm(내가티.stem)

# 내용
내용.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^내용*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^내용*", names(ko.dtm), value=T)))
ko.dtm$내용.stem <- 내용.stem
rm(내용.stem)

# 노동자
노동자.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^노동자*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^노동자*", names(ko.dtm), value=T)))
ko.dtm$노동자.stem <- 노동자.stem
rm(노동자.stem)

# 노무현
노무현.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^노무현*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^노무현*", names(ko.dtm), value=T)))
ko.dtm$노무현.stem <- 노무현.stem
rm(노무현.stem)

# 다까, 다카 (다카키 마사오)
다까.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^다까*", names(ko.dtm), value=T)], na.rm = T)
다카.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^다카*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^다까*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^다카*", names(ko.dtm), value=T)))
ko.dtm$다까.stem <- 다까.stem + 다카.stem
rm(다까.stem); rm(다카.stem)

# 다운계약
다운계약.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^다운계약*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^다운계약*", names(ko.dtm), value=T)))
ko.dtm$다운계약.stem <- 다운계약.stem
rm(다운계약.stem)

# 당황
당황.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^당황*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^당황*", names(ko.dtm), value=T)))
ko.dtm$당황.stem <- 당황.stem
rm(당황.stem)

# 대단
대단.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^대단*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^대단*", names(ko.dtm), value=T)))
ko.dtm$대단.stem <- 대단.stem
rm(대단.stem)

# # 대박
# 대박.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^대박*", names(ko.dtm), value=T)], na.rm = T)
# ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^대박*", names(ko.dtm), value=T)))
# ko.dtm$대박.stem <- 대박.stem
# rm(대박.stem)

# 대통령
대통령.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^대통령*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^대통령*", names(ko.dtm), value=T)))
ko.dtm$대통령.stem <- 대통령.stem
rm(대통령.stem)

# 대한민국
대한민국.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^대한민국*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^대한민국*", names(ko.dtm), value=T)))
ko.dtm$대한민국.stem <- 대한민국.stem
rm(대한민국.stem)

# 독재
독재.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^독재*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^독재*", names(ko.dtm), value=T)))
ko.dtm$독재.stem <- 독재.stem
rm(독재.stem)

# 돌직구
돌직구.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^돌직구*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^돌직구*", names(ko.dtm), value=T)))
ko.dtm$돌직구.stem <- 돌직구.stem
rm(돌직구.stem)

# 드러
드러.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^드러*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^드러*", names(ko.dtm), value=T)))
ko.dtm$드러.stem <- 드러.stem
rm(드러.stem)

# 등록금
등록금.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^등록금*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^등록금*", names(ko.dtm), value=T)))
ko.dtm$등록금.stem <- 등록금.stem
rm(등록금.stem)

# 떨어뜨, 떨어트
떨어뜨.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^떨어뜨*", names(ko.dtm), value=T)], na.rm = T)
떨어트.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^떨어트*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^떨어뜨*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^떨어트*", names(ko.dtm), value=T)))
ko.dtm$떨어뜨.stem <- 떨어뜨.stem + 떨어트.stem
rm(떨어뜨.stem); rm(떨어트.stem)

# 리정희
리정희.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^리정희*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^리정희*", names(ko.dtm), value=T)))
ko.dtm$리정희.stem <- 리정희.stem
rm(리정희.stem)

# # 마리앙
# 마리앙.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^마리앙*", names(ko.dtm), value=T)], na.rm = T)
# ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^마리앙*", names(ko.dtm), value=T)))
# ko.dtm$마리앙.stem <- 마리앙.stem
# rm(마리앙.stem)

# 문재인, 문후보
문재인.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^문재인*", names(ko.dtm), value=T)], na.rm = T)
문후보.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^문후보*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^문재인*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^문후보*", names(ko.dtm), value=T)))
ko.dtm$문재인.stem <- 문재인.stem + 문후보.stem
rm(문재인.stem); rm(문후보.stem)

# 문죄인
문죄인.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^문죄인*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^문죄인*", names(ko.dtm), value=T)))
ko.dtm$문죄인.stem <- 문죄인.stem
rm(문죄인.stem)

# 모르
모르.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^모르*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^모르*", names(ko.dtm), value=T)))
ko.dtm$모르.stem <- 모르.stem
rm(모르.stem)

# 민주당
민주당.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^민주당*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^민주당*", names(ko.dtm), value=T)))
ko.dtm$민주당.stem <- 민주당.stem
rm(민주당.stem)

# 박그네
박그네.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^박그네*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^박그네*", names(ko.dtm), value=T)))
ko.dtm$박그네.stem <- 박그네.stem
rm(박그네.stem)

# 박근혜, 박후보
박근혜.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^박근혜*", names(ko.dtm), value=T)], na.rm = T)
박후보.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^박후보*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^박근혜*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^박후보*", names(ko.dtm), value=T)))
ko.dtm$박근혜.stem <- 박근혜.stem + 박후보.stem
rm(박근혜.stem); rm(박후보.stem)

# 박정희
박정희.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^박정희*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^박정희*", names(ko.dtm), value=T)))
ko.dtm$박정희.stem <- 박정희.stem
rm(박정희.stem)

# 북한
북한.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^북한*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^북한*", names(ko.dtm), value=T)))
ko.dtm$북한.stem <- 북한.stem
rm(북한.stem)

# 불쌍
불쌍.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^불쌍*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^불쌍*", names(ko.dtm), value=T)))
ko.dtm$불쌍.stem <- 불쌍.stem
rm(불쌍.stem)

# 비난
비난.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^비난*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^비난*", names(ko.dtm), value=T)))
ko.dtm$비난.stem <- 비난.stem
rm(비난.stem)

# # 비방
# 비방.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^비방*", names(ko.dtm), value=T)], na.rm = T)
# ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^비방*", names(ko.dtm), value=T)))
# ko.dtm$비방.stem <- 비방.stem
# rm(비방.stem)

# 빨갱
빨갱.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^빨갱*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^빨갱*", names(ko.dtm), value=T)))
ko.dtm$빨갱.stem <- 빨갱.stem
rm(빨갱.stem)

# 사람들
사람들.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^사람들*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^사람들*", names(ko.dtm), value=T)))
ko.dtm$사람들.stem <- 사람들.stem
rm(사람들.stem)

# 사퇴
사퇴.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^사퇴*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^사퇴*", names(ko.dtm), value=T)))
ko.dtm$사퇴.stem <- 사퇴.stem
rm(사퇴.stem)

# 사회자
사회자.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^사회자*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^사회자*", names(ko.dtm), value=T)))
ko.dtm$사회자.stem <- 사회자.stem
rm(사회자.stem)

# 사회환원
사회환원.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^사회환원*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^사회환원*", names(ko.dtm), value=T)))
ko.dtm$사회환원.stem <- 사회환원.stem
rm(사회환원.stem)

# 삼성장
삼성장.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^삼성장*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^삼성장*", names(ko.dtm), value=T)))
ko.dtm$삼성장.stem <- 삼성장.stem
rm(삼성장.stem)

# 선관위
선관위.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^선관위*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^선관위*", names(ko.dtm), value=T)))
ko.dtm$선관위.stem <- 선관위.stem
rm(선관위.stem)

# 소름
소름.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^소름*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^소름*", names(ko.dtm), value=T)))
ko.dtm$소름.stem <- 소름.stem
rm(소름.stem)

# # 스나이퍼
# 스나이퍼.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^스나이퍼*", names(ko.dtm), value=T)], na.rm = T)
# ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^스나이퍼*", names(ko.dtm), value=T)))
# ko.dtm$스나이퍼.stem <- 스나이퍼.stem
# rm(스나이퍼.stem)

# 손석희
손석희.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^손석희*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^손석희*", names(ko.dtm), value=T)))
ko.dtm$손석희.stem <- 손석희.stem
rm(손석희.stem)

# 새누리
새누리.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^새누리*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^새누리*", names(ko.dtm), value=T)))
ko.dtm$새누리.stem <- 새누리.stem
rm(새누리.stem)

# 안보
안보.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^안보*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^안보*", names(ko.dtm), value=T)))
ko.dtm$안보.stem <- 안보.stem
rm(안보.stem)

# 안철수
안철수.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^안철수*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^안철수*", names(ko.dtm), value=T)))
ko.dtm$안철수.stem <- 안철수.stem
rm(안철수.stem)

# 여성대통령
여성대.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^여성대*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^여성대*", names(ko.dtm), value=T)))
ko.dtm$여성대.stem <- 여성대.stem
rm(여성대.stem)

# 영해
영해.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^영해*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^영해*", names(ko.dtm), value=T)))
ko.dtm$영해.stem <- 영해.stem
rm(영해.stem)

# 예능
예능.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^예능*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^예능*", names(ko.dtm), value=T)))
ko.dtm$예능.stem <- 예능.stem
rm(예능.stem)

# 유신
유신.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^유신*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^유신*", names(ko.dtm), value=T)))
ko.dtm$유신.stem <- 유신.stem
rm(유신.stem)

# 이정희, 이후보
이정희.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^이정희*", names(ko.dtm), value=T)], na.rm = T)
이후보.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^이후보*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^이정희*", names(ko.dtm), value=T)))
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^이후보*", names(ko.dtm), value=T)))
ko.dtm$이정희.stem <- 이정희.stem + 이후보.stem
rm(이정희.stem); rm(이후보.stem)

# 전두환
전두환.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^전두환*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^전두환*", names(ko.dtm), value=T)))
ko.dtm$전두환.stem <- 전두환.stem
rm(전두환.stem)

# 정권교체
정권교체.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^정권교체*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^정권교체*", names(ko.dtm), value=T)))
ko.dtm$정권교체.stem <- 정권교체.stem
rm(정권교체.stem)

# 종북
종북.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^종북*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^종북*", names(ko.dtm), value=T)))
ko.dtm$종북.stem <- 종북.stem
rm(종북.stem)

# 참여정
참여정.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^참여정*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^참여정*", names(ko.dtm), value=T)))
ko.dtm$참여정.stem <- 참여정.stem
rm(참여정.stem)

# 청와대
청와대.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^청와대*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^청와대*", names(ko.dtm), value=T)))
ko.dtm$청와대.stem <- 청와대.stem
rm(청와대.stem)

# ㅋㅋ
ㅋㅋ.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^ㅋㅋ*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^ㅋㅋ*", names(ko.dtm), value=T)))
ko.dtm$ㅋㅋ.stem <- ㅋㅋ.stem
rm(ㅋㅋ.stem)

# 토론
토론.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^토론*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^토론*", names(ko.dtm), value=T)))
ko.dtm$토론.stem <- 토론.stem
rm(토론.stem)

# ko.dtm$토론.stem <- rowSums(ko.dtm[,names(ko.dtm) %in% grep("^토론[ 가까과도만ㅇ에으은을의이인일입장ㅋ하한할회 ]", names(ko.dtm), value=T)], na.rm = T)
# ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^토론[가까과도만ㅇ에으은을의이인일입장ㅋ하한할회 ]", names(ko.dtm), value=TRUE)))

# 통진당
통진당.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^통진당*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^통진당*", names(ko.dtm), value=T)))
ko.dtm$통진당.stem <- 통진당.stem
rm(통진당.stem)

# 트위터
트위터.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^트위터*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^트위터*", names(ko.dtm), value=T)))
ko.dtm$트위터.stem <- 트위터.stem
rm(트위터.stem)

# 한미f
한미f.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^한미f*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^한미f*", names(ko.dtm), value=T)))
ko.dtm$한미f.stem <- 한미f.stem
rm(한미f.stem)

# 후보
후보.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^후보*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^후보*", names(ko.dtm), value=T)))
ko.dtm$후보.stem <- 후보.stem
rm(후보.stem)

# h.park20
h.park20.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^h.park20*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^h.park20*", names(ko.dtm), value=T)))
ko.dtm$h.park20.stem <- h.park20.stem
rm(h.park20.stem)

# h.대선토
h.대선토.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^h.대선토*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^h.대선토*", names(ko.dtm), value=T)))
ko.dtm$h.대선토.stem <- h.대선토.stem
rm(h.대선토.stem)

# h.박근
h.박근.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^h.박근*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^h.박근*", names(ko.dtm), value=T)))
ko.dtm$h.박근.stem <- h.박근.stem
rm(h.박근.stem)

# h.위키트
h.위키트.stem <- rowSums(ko.dtm[, names(ko.dtm) %in% grep("^h.위키트*", names(ko.dtm), value=T)], na.rm = T)
ko.dtm <- subset(ko.dtm, select = !(names(ko.dtm) %in% grep("^h.위키트*", names(ko.dtm), value=T)))
ko.dtm$h.위키트.stem <- h.위키트.stem
rm(h.위키트.stem)

# Remove variables that is longer than 15 characters
ko.dtm <- subset(ko.dtm, select = !str_length(names(ko.dtm)) > 10)



ko.dtm <- 
  cbind(d.coded.2$Coding, ko.dtm)
names(ko.dtm)[1] <- "User_Ideology"

write.table(ko.dtm, "ko.dtm.noname.csv", sep = ",", col.names = F)
# write.csv(ko.dtm, "ko.dtm.csv")

# training_dtm_combined$conservative <-
#   training_dtm_combined$conservative + training_dtm_combined$conservatives +
#   training_dtm_combined$conservatism + training_dtm_combined$conservatarian
# training_dtm_combined$conservatives <- NULL
# training_dtm_combined$conservatism <- NULL
# training_dtm_combined$conservatarian <- NULL

# ko.dtm <- DocumentTermMatrix(koCorpus)
# findFreqTerms(ko.dtm, 15)
# sort(colSums(inspect(ko.dtm)), decreasing = F)
# http://blog.daum.net/revisioncrm/180


```


#### Divide data into training and test set using caret() package
**Put this after all manual stemming process**

```{r create training/test set}
library(caret)
inTrain <- createDataPartition(y = ko.dtm$User_Ideology, p = .75, list = F)
ko.dtm.train <- ko.dtm[inTrain, ]
ko.dtm.test <- ko.dtm[-inTrain, ]
```
