---
title: "02 Data Prep - Whole Data"
author: "JungHwan Yang"
date: "May 2, 2015"
output: html_document
---

```{r}
# Merge cells with some errors
d2$V3 <- paste(d2$V3, d2$V30, sep = ""); d2$V30 <- NULL
d2$V9 <- paste(d2$V9, d2$V90, sep = ""); d2$V90 <- NULL


# Apply clearText() to every line
d2$text <- sapply(d2$V3, cleanText)
koCorpus.whole <- Corpus(VectorSource(d2$text))

ko.whole.dtm <- data.frame(inspect(DocumentTermMatrix(koCorpus.whole)))

# Merge unique ID with DTM
ko.whole.dtm <- 
  cbind(d2$V1, ko.whole.dtm)
names(ko.whole.dtm)[1] <- "UniqueID"

# Change the variable names of the hashtag DTM by replacing # with h.
names (ko.whole.dtm) <-
  names(ko.whole.dtm) %>%
  gsub("X.", "h.", .)

# Remove weird X
names (ko.whole.dtm) <-
  names(ko.whole.dtm) %>%
  gsub("X", "", .)

# 국민
국민.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^국민*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^국민*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$국민.stem <- 국민.stem
rm(국민.stem)

# 궁금
궁금.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^궁금*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^궁금*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$궁금.stem <- 궁금.stem
rm(궁금.stem)

# 공산
공산.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^공산*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^공산*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$공산.stem <- 공산.stem
rm(공산.stem)

# 나왔
나왔.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^나왔*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^나왔*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$나왔.stem <- 나왔.stem
rm(나왔.stem)

# 날치기
날치기.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^날치기*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^날치기*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$날치기.stem <- 날치기.stem
rm(날치기.stem)

# 남북관계
남북관계.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^남북관계*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^남북관계*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$남북관계.stem <- 남북관계.stem
rm(남북관계.stem)

# 남쪽정부, 남한정부
남쪽정부.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^남쪽정부*", names(ko.whole.dtm), value=T)], na.rm = T)
남한정부.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^남한정부*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^남쪽정부*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^남한정부*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$남쪽정부.stem <- 남쪽정부.stem + 남한정부.stem
rm(남쪽정부.stem); rm(남한정부.stem)

# 내거티, 내가티
내거티.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^내거티*", names(ko.whole.dtm), value=T)], na.rm = T)
내가티.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^내가티*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^내거티*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^내가티*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$내거티.stem <- 내거티.stem + 내가티.stem
rm(내거티.stem); rm(내가티.stem)

# 내용
내용.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^내용*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^내용*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$내용.stem <- 내용.stem
rm(내용.stem)

# 노동자
노동자.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^노동자*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^노동자*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$노동자.stem <- 노동자.stem
rm(노동자.stem)

# 노무현
노무현.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^노무현*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^노무현*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$노무현.stem <- 노무현.stem
rm(노무현.stem)

# 다까, 다카 (다카키 마사오)
다까.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^다까*", names(ko.whole.dtm), value=T)], na.rm = T)
다카.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^다카*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^다까*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^다카*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$다까.stem <- 다까.stem + 다카.stem
rm(다까.stem); rm(다카.stem)

# 다운계약
다운계약.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^다운계약*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^다운계약*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$다운계약.stem <- 다운계약.stem
rm(다운계약.stem)

# 당황
당황.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^당황*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^당황*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$당황.stem <- 당황.stem
rm(당황.stem)

# 대단
대단.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^대단*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^대단*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$대단.stem <- 대단.stem
rm(대단.stem)

# 대박
대박.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^대박*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^대박*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$대박.stem <- 대박.stem
rm(대박.stem)

# 대통령
대통령.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^대통령*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^대통령*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$대통령.stem <- 대통령.stem
rm(대통령.stem)

# 대한민국
대한민국.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^대한민국*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^대한민국*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$대한민국.stem <- 대한민국.stem
rm(대한민국.stem)

# 독재
독재.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^독재*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^독재*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$독재.stem <- 독재.stem
rm(독재.stem)

# 돌직구
돌직구.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^돌직구*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^돌직구*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$돌직구.stem <- 돌직구.stem
rm(돌직구.stem)

# 드러
드러.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^드러*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^드러*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$드러.stem <- 드러.stem
rm(드러.stem)

# 등록금
등록금.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^등록금*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^등록금*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$등록금.stem <- 등록금.stem
rm(등록금.stem)

# 떨어뜨, 떨어트
떨어뜨.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^떨어뜨*", names(ko.whole.dtm), value=T)], na.rm = T)
떨어트.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^떨어트*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^떨어뜨*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^떨어트*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$떨어뜨.stem <- 떨어뜨.stem + 떨어트.stem
rm(떨어뜨.stem); rm(떨어트.stem)

# 리정희
리정희.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^리정희*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^리정희*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$리정희.stem <- 리정희.stem
rm(리정희.stem)

# 마리앙
마리앙.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^마리앙*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^마리앙*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$마리앙.stem <- 마리앙.stem
rm(마리앙.stem)

# 문재인, 문후보
문재인.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^문재인*", names(ko.whole.dtm), value=T)], na.rm = T)
문후보.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^문후보*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^문재인*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^문후보*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$문재인.stem <- 문재인.stem + 문후보.stem
rm(문재인.stem); rm(문후보.stem)

# 문죄인
문죄인.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^문죄인*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^문죄인*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$문죄인.stem <- 문죄인.stem
rm(문죄인.stem)

# 모르
모르.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^모르*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^모르*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$모르.stem <- 모르.stem
rm(모르.stem)

# 민주당
민주당.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^민주당*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^민주당*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$민주당.stem <- 민주당.stem
rm(민주당.stem)

# 박그네
박그네.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^박그네*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^박그네*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$박그네.stem <- 박그네.stem
rm(박그네.stem)

# 박근혜, 박후보
박근혜.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^박근혜*", names(ko.whole.dtm), value=T)], na.rm = T)
박후보.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^박후보*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^박근혜*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^박후보*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$박근혜.stem <- 박근혜.stem + 박후보.stem
rm(박근혜.stem); rm(박후보.stem)

# 박정희
박정희.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^박정희*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^박정희*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$박정희.stem <- 박정희.stem
rm(박정희.stem)

# 북한
북한.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^북한*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^북한*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$북한.stem <- 북한.stem
rm(북한.stem)

# 불쌍
불쌍.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^불쌍*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^불쌍*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$불쌍.stem <- 불쌍.stem
rm(불쌍.stem)

# 비난
비난.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^비난*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^비난*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$비난.stem <- 비난.stem
rm(비난.stem)

# 비방
비방.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^비방*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^비방*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$비방.stem <- 비방.stem
rm(비방.stem)

# 빨갱
빨갱.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^빨갱*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^빨갱*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$빨갱.stem <- 빨갱.stem
rm(빨갱.stem)

# 사람들
사람들.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^사람들*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^사람들*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$사람들.stem <- 사람들.stem
rm(사람들.stem)

# 사퇴
사퇴.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^사퇴*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^사퇴*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$사퇴.stem <- 사퇴.stem
rm(사퇴.stem)

# 사회자
사회자.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^사회자*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^사회자*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$사회자.stem <- 사회자.stem
rm(사회자.stem)

# 사회환원
사회환원.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^사회환원*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^사회환원*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$사회환원.stem <- 사회환원.stem
rm(사회환원.stem)

# 삼성장
삼성장.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^삼성장*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^삼성장*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$삼성장.stem <- 삼성장.stem
rm(삼성장.stem)

# 선관위
선관위.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^선관위*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^선관위*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$선관위.stem <- 선관위.stem
rm(선관위.stem)

# 소름
소름.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^소름*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^소름*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$소름.stem <- 소름.stem
rm(소름.stem)

# 스나이퍼
스나이퍼.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^스나이퍼*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^스나이퍼*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$스나이퍼.stem <- 스나이퍼.stem
rm(스나이퍼.stem)

# 손석희
손석희.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^손석희*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^손석희*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$손석희.stem <- 손석희.stem
rm(손석희.stem)

# 새누리
새누리.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^새누리*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^새누리*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$새누리.stem <- 새누리.stem
rm(새누리.stem)

# 안보
안보.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^안보*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^안보*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$안보.stem <- 안보.stem
rm(안보.stem)

# 안철수
안철수.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^안철수*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^안철수*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$안철수.stem <- 안철수.stem
rm(안철수.stem)

# 여성대통령
여성대.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^여성대*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^여성대*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$여성대.stem <- 여성대.stem
rm(여성대.stem)

# 영해
영해.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^영해*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^영해*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$영해.stem <- 영해.stem
rm(영해.stem)

# 예능
예능.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^예능*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^예능*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$예능.stem <- 예능.stem
rm(예능.stem)

# 유신
유신.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^유신*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^유신*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$유신.stem <- 유신.stem
rm(유신.stem)

# 이정희, 이후보
이정희.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^이정희*", names(ko.whole.dtm), value=T)], na.rm = T)
이후보.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^이후보*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^이정희*", names(ko.whole.dtm), value=T)))
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^이후보*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$이정희.stem <- 이정희.stem + 이후보.stem
rm(이정희.stem); rm(이후보.stem)

# 전두환
전두환.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^전두환*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^전두환*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$전두환.stem <- 전두환.stem
rm(전두환.stem)

# 정권교체
정권교체.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^정권교체*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^정권교체*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$정권교체.stem <- 정권교체.stem
rm(정권교체.stem)

# 종북
종북.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^종북*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^종북*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$종북.stem <- 종북.stem
rm(종북.stem)

# 참여정
참여정.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^참여정*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^참여정*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$참여정.stem <- 참여정.stem
rm(참여정.stem)

# 청와대
청와대.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^청와대*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^청와대*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$청와대.stem <- 청와대.stem
rm(청와대.stem)

# ㅋㅋ
ㅋㅋ.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^ㅋㅋ*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^ㅋㅋ*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$ㅋㅋ.stem <- ㅋㅋ.stem
rm(ㅋㅋ.stem)

# 토론
토론.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^토론*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^토론*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$토론.stem <- 토론.stem
rm(토론.stem)

# ko.whole.dtm$토론.stem <- rowSums(ko.whole.dtm[,names(ko.whole.dtm) %in% grep("^토론[ 가까과도만ㅇ에으은을의이인일입장ㅋ하한할회 ]", names(ko.whole.dtm), value=T)], na.rm = T)
# ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^토론[가까과도만ㅇ에으은을의이인일입장ㅋ하한할회 ]", names(ko.whole.dtm), value=TRUE)))

# 통진당
통진당.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^통진당*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^통진당*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$통진당.stem <- 통진당.stem
rm(통진당.stem)

# 트위터
트위터.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^트위터*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^트위터*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$트위터.stem <- 트위터.stem
rm(트위터.stem)

# 한미f
한미f.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^한미f*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^한미f*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$한미f.stem <- 한미f.stem
rm(한미f.stem)

# 후보
후보.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^후보*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^후보*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$후보.stem <- 후보.stem
rm(후보.stem)

# h.park20
h.park20.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^h.park20*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^h.park20*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$h.park20.stem <- h.park20.stem
rm(h.park20.stem)

# h.대선토
h.대선토.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^h.대선토*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^h.대선토*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$h.대선토.stem <- h.대선토.stem
rm(h.대선토.stem)

# h.박근
h.박근.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^h.박근*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^h.박근*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$h.박근.stem <- h.박근.stem
rm(h.박근.stem)

# h.위키트
h.위키트.stem <- rowSums(ko.whole.dtm[, names(ko.whole.dtm) %in% grep("^h.위키트*", names(ko.whole.dtm), value=T)], na.rm = T)
ko.whole.dtm <- subset(ko.whole.dtm, select = !(names(ko.whole.dtm) %in% grep("^h.위키트*", names(ko.whole.dtm), value=T)))
ko.whole.dtm$h.위키트.stem <- h.위키트.stem
rm(h.위키트.stem)

# Remove variables that is longer than 15 characters
library(stringr)
ko.whole.dtm <- subset(ko.whole.dtm, select = !str_length(names(ko.whole.dtm)) > 10)

```

Total number of variables in DTM reduced from 66395 to 50478


### Add time variable to the data frame

```{r}
ko.whole.dtm <- 
  cbind(d2$V2, ko.whole.dtm)
names(ko.whole.dtm)[1] <- "time"
```


# Subset data frame more

- It seems like the debate starts at 2012-12-04 11:00:25 (Twitter time, which is 20:00:25 in Korean time.)
- The first tweet that mentioned the start of the debate was 11:00:33
- Here, I subset the data from 10 minutes from the start point and 10 minutes after the end point of the debate
- The debate lasted for 1:53:09
- The end time would be 12:53:34 (12:54:00 for we used 30 sec interval)
- The total time range of the data would be:
    - 10:50:30 ~ 13:04:00

```{r}
# Subset two hours (2:20 hours)
ko.whole.dtm <- 
  subset(ko.whole.dtm,
         as.POSIXct(time) > '2012-12-04 10:50:29' &
         as.POSIXct(time) < '2012-12-04 13:04:01')
# This results in 21815 observations

d2.1 <- 
  subset(d2,
         as.POSIXct(V2) > '2012-12-04 10:50:29' &
         as.POSIXct(V2) < '2012-12-04 13:04:01')
```

Group time by 30 seconds

```{r}
time.30 <- cut(as.POSIXct(ko.whole.dtm[,"time"]),
               breaks = '30 sec', ordered_result = T)
ko.whole.dtm <- 
  cbind(time.30, ko.whole.dtm)
names(ko.whole.dtm)[1] <- "time.30"
rm(time.30)
```


```{r}
# Shorted the list of variables of ko.whole.dtm by only using the variables that are used in the handcoded training data.
ko.whole.dtm.short <-
  subset(ko.whole.dtm, select = (names(ko.whole.dtm) %in% names(ko.dtm)))

ko.dtm.short <-
  subset(ko.dtm, select = (names(ko.dtm) %in% names(ko.whole.dtm)))
ko.dtm.short <- 
  cbind(d.coded.2$Coding, ko.dtm.short)
names(ko.dtm.short)[1] <- "User_Ideology"


ko.dtm.names <- names(ko.dtm.short)

write.table(ko.dtm.short, "ko.dtm.noname.csv", sep = ",", col.names = F)
write.table(ko.whole.dtm.short, "ko.whole.dtm.noname.csv", sep = ",", col.names = F)
write.table(ko.dtm.names, "variable.names.csv")
```

http://stackoverflow.com/questions/13649019/with-r-split-time-series-data-into-time-intervals-say-an-hour-and-then-plot-t
http://r.789695.n4.nabble.com/How-to-sum-and-group-data-by-DATE-in-data-frame-td903708.html
http://stackoverflow.com/questions/14236349/how-to-sum-5-minute-intervals-in-r
http://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf


### Combining machine coded column with the dtm

```{r}
# Combining trained coding with the DTM
ko.class <- read.csv("ML Results/class_predictions.csv", header = F)
## First column of this file contains the result of Ridge clasifier, Random Forest (2nd col), SVM (3rd)
colnames(ko.class) <- c("Ridge", "RandomF", "SVM")
ko.class$classC <- 0
ko.class$classL <- 0
ko.class$classU <- 0
ko.class$classM <- 0

# Change nominal variable to binary variable
ko.class$classC <- ifelse(ko.class$Ridge == "C", 1, 0)
ko.class$classL <- ifelse(ko.class$Ridge == "L", 1, 0)
ko.class$classU <- ifelse(ko.class$Ridge == "U", 1, 0)
ko.class$classM <- ifelse(ko.class$Ridge == "M", 1, 0)

# Remove the first row of ko.whole.dtm.short
ko.whole.dtm.short <- ko.whole.dtm.short[-1,]
d2.1 <- d2.1[-1,]

# Combine classification
ko.whole.dtm.short <- 
  cbind(ko.class[4:7], ko.whole.dtm.short)

# Combining time.30 (time variable group by 30 secs) with the trained set
ko.whole.dtm.short <- 
  cbind(d2.1$V2, ko.whole.dtm.short)
ko.whole.dtm.short <- ko.whole.dtm.short[-c(1:7),] # Delete first 7 tweets to adjust start time
names(ko.whole.dtm.short)[1] <- "time.30"
ko.whole.dtm.short$time.30 <- 
  cut(as.POSIXct(ko.whole.dtm.short[,"time.30"]),
      breaks = '30 sec', ordered_result = T)
```


```{r}
ko.whole.grouped <- group_by(ko.whole.dtm.short, time.30)
ko.whole.grouped <- summarise_each(ko.whole.grouped, funs(sum))

ko.whole.grouped$count.seg <- 
  ko.whole.grouped$classC + ko.whole.grouped$classL +
  ko.whole.grouped$classU + ko.whole.grouped$classM

ko.whole.grouped$communist.key <-
  ko.whole.grouped$공산.stem + ko.whole.grouped$빨갱.stem +
  ko.whole.grouped$종북.stem

ko.whole.grouped <- ko.whole.grouped[c(1, 4965, 2:4964)]
ko.whole.grouped <- data.frame(ko.whole.grouped)

ko.whole.grouped$time.30 <-
  as.POSIXct(ko.whole.grouped$time.30) + 32400 #adjust time

# ko.whole.grouped$time.30 <-
#   strftime(as.POSIXct(ko.whole.grouped$time.30), "%H:%M:%S")
```

### Make a time lagged datasets

#### 15 secs lagged data

```{r}
##### 15 secs lagged dataset

# Shorted the list of variables of ko.whole.dtm by only using the variables that are used in the handcoded training data.
ko.whole.dtm.short.15 <- # Make a 15 sec lagged dataset
  subset(ko.whole.dtm, select = (names(ko.whole.dtm) %in% names(ko.dtm)))

# Remove the first row of ko.whole.dtm.short
ko.whole.dtm.short.15 <- ko.whole.dtm.short.15[-1,]

# Combine classification
ko.whole.dtm.short.15 <- 
  cbind(ko.class[4:7], ko.whole.dtm.short.15)

# Combining time.15 (time variable group by 15 secs) with the trained set
ko.whole.dtm.short.15 <- 
  cbind(d2.1$V2, ko.whole.dtm.short.15)
ko.whole.dtm.short.15 <- ko.whole.dtm.short.15[-c(1:7),] # Delete first 7 tweets to adjust start time

names(ko.whole.dtm.short.15)[1] <- "time.15.lag15"

# Group by 15 secs
ko.whole.dtm.short.15$time.15.lag15 <- 
  cut(as.POSIXct(ko.whole.dtm.short.15[,"time.15.lag15"]),
      breaks = '15 sec', ordered_result = T)

# Then remove the first six cases that belong to the 15 sec segment and grouped by 30 secs
ko.whole.dtm.short.15 <- ko.whole.dtm.short.15[-c(1:6),]

ko.whole.dtm.short.15$time.15.lag15 <-
  cut(as.POSIXct(ko.whole.dtm.short.15[, "time.15.lag15"]),
      breaks = '30 sec', ordered_result = T)
names(ko.whole.dtm.short.15)[1] <- "time.30.lag15"

# Summarize by 30 secs
ko.whole.grouped.15 <- group_by(ko.whole.dtm.short.15, time.30.lag15)
ko.whole.grouped.15 <- summarise_each(ko.whole.grouped.15, funs(sum))

ko.whole.grouped.15$communist.key <-
  ko.whole.grouped.15$공산.stem + ko.whole.grouped.15$빨갱.stem +
  ko.whole.grouped.15$종북.stem

ko.whole.grouped.15$count.seg <- 
  ko.whole.grouped.15$classC + ko.whole.grouped.15$classL +
  ko.whole.grouped.15$classU + ko.whole.grouped.15$classM

ko.whole.grouped.15 <- ko.whole.grouped.15[c(1, 4966, 2:4965)]
ko.whole.grouped.15 <- data.frame(ko.whole.grouped.15)

ko.whole.grouped.15$time.30.lag15 <-
  as.POSIXct(ko.whole.grouped.15$time.30.lag15) + 32400 #adjust time
```

#### 30 secs lagged data

- Use non-lagged data and put 30 secs lag

```{r}
ko.whole.grouped.30 <- ko.whole.grouped[-1, ]
```

#### 45 secs lagged data

- Use 15 secs-lagged data and put 30 secs lag

```{r}
ko.whole.grouped.45 <- ko.whole.grouped.15[-1, ]
```

