---
title: "03 Plotting Time Series"
author: "JungHwan Yang"
date: "May 7, 2015"
output: html_document
---


```{r}

plot(ko.whole.grouped$time.30, ko.whole.grouped$count.seg)

ggplot(ko.whole.grouped, aes(x=time.30, y=count.seg)) + geom_line()

library(ggplot2)

# Total volume
plotTot <-
  ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) + 
  geom_line(aes(y = count.seg, col = "Total count")) +
  xlab("Time") + ylab("Count") + 
  theme_bw() 
 

plotTot.1 <-
  ggplot(ko.whole.grouped, aes(x = time.30, y = count.seg)) + 
  geom_point() + geom_smooth(method = "loess") +
  xlab("Time") + ylab("Count") + 
  theme_bw()


# Conservative and Liberal
plotCL.count <- 
  ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) + 
  geom_line(aes(y = classC, col = "Conservative")) + 
  geom_line(aes(y = classL, col = "Liberal")) +
  xlab("Time") + ylab("Count") +
  theme_bw() 

plotCL.count.1 <- 
  ggplot(ko.whole.grouped, aes(x = time.30, y = , color = Type)) + 
  geom_point(aes(y = classC, col = "Conservative")) + 
  geom_point(aes(y = classL, col = "Liberal")) +
  geom_smooth(aes(y = classC, col = "Conservative"), method = "loess") + 
  geom_smooth(aes(y = classL, col = "Liberal"), method = "loess") +
  xlab("Time") + ylab("Count") +
  theme_bw()

  
plotCL.prop <- 
  ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) + 
  geom_line(aes(y = classC/count.seg, col = "Conservative")) + 
  geom_line(aes(y = classL/count.seg, col = "Liberal")) +
  xlab("Time") + ylab("Count") +
  theme_bw()


# Memes
plotM <-
  ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) +
  geom_line(aes(y = classM, col = "Memes         ")) + 
  xlab("Time") + ylab("Count") +
  theme_bw()


# Plot popular keywords
# Find popular terms
sort(colSums(ko.whole.grouped[,-1]))

# Candidates' names
plotNames <-
  ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) +
  geom_line(aes(y = 이정희.stem, col = "Lee             ")) + 
  geom_line(aes(y = 박근혜.stem, col = "Park            ")) +
  geom_line(aes(y = 문재인.stem, col = "Moon            ")) +
  xlab("Time") + ylab("Count") +
  theme_bw()

plotMemes <-
  ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) +
  geom_line(aes(y = 사퇴.stem, col = "Withdraw")) +
  geom_line(aes(y = 다까.stem, col = "Dakaki Masao")) + 
  geom_line(aes(y = 떨어뜨.stem, col = "Defeat You")) +
  xlab("Time") + ylab("Count") +
  theme_bw()

  
  

# # Not very many tweets with these
# ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) +
#   geom_line(aes(y = 리정희.stem, col = "Lee (mockery)")) + 
#   geom_line(aes(y = 박그네.stem, col = "Park (mockery)")) +
#   geom_line(aes(y = 문죄인.stem, col = "Moon (mockery)")) +
#   xlab("Time") + ylab("Count") +
#   theme_bw()


# Plotting main keywords/memes

ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) +
  geom_line(aes(y = 종북.stem+공산.stem+빨갱.stem, col = "Communist")) +
  geom_line(aes(y = 다까.stem, col = "Dakaki Masao")) + 
  geom_line(aes(y = 읽을게, col = "Eval")) +
  geom_line(aes(y = 떨어뜨.stem, col = "Defeat You")) +
  xlab("Time") + ylab("Count") +
  theme_bw()


ggplot(ko.whole.grouped, aes(time.30, y = value, color = Type)) +
  geom_line(aes(y = count.seg, col = "Tot")) +
  geom_line(aes(y = 떨어뜨.stem, col = "Defeat You")) +
  xlab("Time") + ylab("Count") +
  theme_bw()

```


Put multiple plots in a page

```{r}
# Multiple plot function
#
# ggplot objects can be passed in ..., or to plotlist (as a list of ggplot objects)
# - cols:   Number of columns in layout
# - layout: A matrix specifying the layout. If present, 'cols' is ignored.
#
# If the layout is something like matrix(c(1,2,3,3), nrow=2, byrow=TRUE),
# then plot 1 will go in the upper left, 2 will go in the upper right, and
# 3 will go all the way across the bottom.
#
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)

  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)

  numPlots = length(plots)

  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }

 if (numPlots==1) {
    print(plots[[1]])

  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))

    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))

      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}
```


```{r}
multiplot(plotNames, plotCL.count, cols=1)
```


ggplot(ko.whole.grouped, aes(time.30, y = value, color = type)) + 
    geom_point(aes(y = 박근혜.stem, col = "park.p")) + 
    geom_point(aes(y = 박그네.stem, col = "park.n")) +
    geom_point(aes(y = 이정희.stem, col = "lee.p")) +
    geom_point(aes(y = 리정희.stem, col = "lee.n")) +
    geom_point(aes(y = 문재인.stem, col = "moon.p")) +
    geom_point(aes(y = 문죄인.stem, col = "moon.n"))
  
  
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
